Combinatorics of the geometry of Wilson loop diagrams

### 2019-01-04 General WLD combinatorics.tex
now with all tex tags actually closed

Talk about Grassmann Necklaces and how it defines a cell in a CW complex of $\Gr(k,n)$. Also talk about how this is exactly all the non-negative matrices that represent a particular positroid.

Also talk about Le diagrams.

@@

Therefore, once again we can see that the $J_r^{(W)}(*)$ are cyclic for all $r\neq p$ in $W$.  Assembling the intervals for $p$ we have:
\begin{itemize}
\item if $m=j$ then
\begin{gather*}J_p^{(W)}(m) = [m+4,e-1], \qquad  J_p^{(W)}(m+1) = [e,m], \\  J_p^{(W)}(m+2) = [m+1,m+2], \qquad  J_p^{(W)}(m+3) = \{m+3\},\end{gather*}
\item if $m=j+1$ then
\begin{gather*}J_p^{(W)}(m) = [m+4,m-1], \qquad J_p^{(W)}(m+1) = [m,m+1], \\  J_p^{(W)}(m+2) = \{m+2\}, \qquad  J_p^{(W)}(m+3) = \{m+3\},\end{gather*}
\item if $m=j+2$ then
\begin{gather*}J_p^{(W)}(m) = [m+4,m], \qquad  J_p^{(W)}(m+1) = \{m+1\}, \\  J_p^{(W)}(m+2) = \{m+2\}, \qquad  J_p^{(W)}(m+3) = \{m+3\}.\end{gather*}
The result now follows by induction.

>>>>

% Talk about Grassmann Necklaces and how it defines a cell in a CW complex of $\Gr(k,n)$. Also talk about how this is exactly all the non-negative matrices that represent a particular positroid.

% Also talk about Le diagrams.

[We probably need a subsection for background here. Probably move the definition of Grassmann necklace up to here, a few words about positroids and Postnikov's work, def of Le diagrams and GNs, why it's useful to be able to translate between WLD, GN, Le diagrams at will. ]

@@

Therefore, once again we can see that the $J_r^{(W)}(*)$ are cyclic for all $r\neq p$ in $W$.  Assembling the intervals for $p$ we have:
\begin{itemize}
\item if $m=j$ then
\begin{gather*}J_p^{(W)}(m) = [m+4,e-1], \qquad  J_p^{(W)}(m+1) = [e,m], \\  J_p^{(W)}(m+2) = [m+1,m+2], \qquad  J_p^{(W)}(m+3) = \{m+3\},\end{gather*}
\item if $m=j+1$ then
\begin{gather*}J_p^{(W)}(m) = [m+4,m-1], \qquad J_p^{(W)}(m+1) = [m,m+1], \\  J_p^{(W)}(m+2) = \{m+2\}, \qquad  J_p^{(W)}(m+3) = \{m+3\},\end{gather*}
\item if $m=j+2$ then
\begin{gather*}J_p^{(W)}(m) = [m+4,m], \qquad  J_p^{(W)}(m+1) = \{m+1\}, \\  J_p^{(W)}(m+2) = \{m+2\}, \qquad  J_p^{(W)}(m+3) = \{m+3\}.\end{gather*}
\end{itemize}
The result now follows by induction.
